Modelling the emergence of whisker barrels

### 2020-07-01 paper/briefpaper/brief.tex
Figure improvements, biggest ones for Fig 5

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape. Low
  overall values of the \emph{Honda-}$\delta$ metric obtained from simulated
  barrels indicate a close correspondence of the simulated barrel field with a
  Voronoi tesselation, and thus with a biological barrel field. For the
  % Run ./build/sim/honda boundaries/rat_barrels/wb_110405_Dirichlet.svg to
  % get this result:
  tesselation overlaid on the real barrel field in Fig.\,1A, $\delta=0.025$,
  and a reduction in the Honda-$\delta$ metric in simulation
  confirmed that an equivalent `good' Voronoi pattern} (see
    \citealp{senft_mouse_1991}) \metrics{emerged within $\approx$~20000
  iterations (Fig.\,\ref{fig:main}D, red circles). Second, we devised a
  \emph{pattern difference} measure that is sensitive to deviations in the
  component shapes and overall topographic registration of two tesselations,
  $\eta$, and we used this measure to compare the simulated barrel fields to
  the real barrel field from which the simulation boundary shape was obtained
  (see Materials and Methods for details). A similar reduction in pattern
  difference over simulation time confirmed that the shapes and arrangement of
  emergent connection fields matched those of the real barrel field by around
  20000 iterations. Third, we measured the \emph{connection selectivity} at
  each location on the cortical sheet, as the connection density of the most
  dense projection divided by the sum over all projection densities, $\omega$.}
%
\metrics{Against these three metrics we are also able to characterise the
  robustness of self-organization to the model parameters, and to investigate
  the sensitivity of the model to variation in its inputs.}

@@

\MPthreePar8u{In Fig.\,\ref{fig:paramsweep}B, we present some patterns
  representing alternative parameter choices. Because the patterns are robust
  to alterations in $\epsilon$ and the choices of $\alpha$ and $\beta$, we
  concentrate our attention on the diffusion constant, $D$. Changing $D$,
  whose value defines the rate at which a region of localized branching will
  spread out across the domain, $S$, is equivalent to making changes to the
  size of $S$ with a fixed branching diffusion rate. These simulations can
  therefore be thought of as representing animals with a varying cortical
  areas but with unchanged cortical complexity. The most extreme example
  (Fig.\,\ref{fig:paramsweep}B iii) could represent an animal with a very
  large cortical area (such as the South American capybara) which receives
  sensory input from $N=41$ thalamic barreloids. Here, a large proportion of
  the domain is occupied by the projections with intermediate interaction
  parameters and those with strong interaction parameters are bunched up
  towards the edge of the domain. In this case, a barrel pattern fails to
  form, agreeing with the observation that cortical whisker barrels are absent
  in the capybara.}

@@

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPtwo{Simulating whisker trimming by reduction of
      $\epsilon$ for the thalamocortical projection for barrel C3, for which
      $i=13$. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{A} Graph of individual barrel measures
      plotted vs.~the multiplier applied to $\epsilon_{13}$. \textbf{B} The
      pattern for $\epsilon_{m}=0.64$.}}
  \label{fig:whiskertrim}
\end{center}

>>>>

% New section to describe and introduce the metrics
\metrics{First, we used an algorithm introduced by Honda to measure the
  discrepancy of each barrel shape from a Dirichletform shape. Low overall
  values of the dimensionless \emph{Honda-}$\delta$ metric (called $\Delta$
  in}
\citealp{honda_geometrical_1983}) \metrics{obtained from simulated barrels indicate a close
  correspondence of the simulated barrel field with a Voronoi tesselation, and
  thus with a biological barrel field. For the
  % Run ./build/sim/honda boundaries/rat_barrels/wb_110405_Dirichlet.svg to
  % get this result:
  tesselation overlaid on the real barrel field in Fig.\,\ref{fig:main}A,
  $\delta=0.025$, and a reduction in the Honda-$\delta$ metric in simulation
  confirmed that an equivalent `good' Voronoi pattern} (see
\citealp{senft_mouse_1991}) \metrics{emerged within $\approx$~20000 iterations
  (Fig.\,\ref{fig:main}D, red circles). Second, we devised a \emph{pattern
    difference} measure that is sensitive to deviations in the component
  shapes and overall topographic registration of two tesselations, $\eta$, and
  we used this measure to compare the simulated barrel fields to the real
  barrel field from which the simulation boundary shape was obtained (see
  Materials and Methods for details). A similar reduction in pattern
  difference over simulation time confirmed that the shapes and arrangement of
  emergent connection fields matched those of the real barrel field by around
  20000 iterations. Third, we measured the \emph{connection selectivity} at
  each location on the cortical sheet, as the connection density of the most
  dense projection divided by the sum over all projection densities,
  $\omega$.}
%
\metrics{Against these three metrics we are also able to characterise the
  robustness of self-organization to the model parameters, and to investigate
  the sensitivity of the model to variation in its inputs.}

@@

\MPthreePar{In Fig.\,\ref{fig:paramsweep}B, we present some patterns
  representing alternative parameter choices. Because the patterns are robust
  to alterations in $\epsilon$ and the choices of $\alpha$ and $\beta$, we
  concentrate our attention on the diffusion constant, $D$. Changing $D$,
  whose value defines the rate at which a region of localized branching will
  spread out across the domain, $S$, is equivalent to making changes to the
  size of $S$ with a fixed branching diffusion rate. These simulations can
  therefore be thought of as representing animals with a varying cortical
  areas but with unchanged cortical complexity. The most extreme example
  (Fig.\,\ref{fig:paramsweep}B iii) could represent an animal with a very
  large cortical area (such as the South American capybara) which receives
  sensory input from $N=41$ thalamic barreloids. Here, a large proportion of
  the domain is occupied by the projections with intermediate interaction
  parameters and those with strong interaction parameters are bunched up
  towards the edge of the domain. In this case, a barrel pattern fails to
  form, agreeing with the observation that cortical whisker barrels are absent
  in the capybara.}

@@

\begin{center}
  \includegraphics[width=\linewidth]{./Fig5.png}
  \captionof{figure}{\MPthreePred{Simulating whisker trimming by reduction of
      $\epsilon$ for the thalamocortical projection for barrel C3, for which
      $i=13$. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{A} Graph of individual barrel measures
      plotted vs.~the multiplier applied to $\epsilon_{13}$. \textbf{B} The
      pattern for $\epsilon_{m}=0.64$.}}
  \label{fig:whiskertrim}
\end{center}
